Retrofitting Effect Handlers onto OCaml

### 2020-11-13 retro-concurrency.tex
tweak

The need to host millions of continuations at the same time rules out the use
of a large contiguous stack space as in C for continuations. Instead, we resort
to using small initial stacks and growing the stacks on demand. As a result,
OCaml functions, irrespective of whether they use effect handlers, need to
perform stack overflow checks and external C functions, which do not have stack
overflow checks, must be performed on a separate system stack. Additionally, we
must generate DWARF stack unwind tables for stacks that may be non-contiguous.
In this work, we develop the compiler and runtime support for implementing
efficient effect handlers for OCaml that satisfy these requirements.

>>>>

The need to host millions of continuations at the same time rules out the use
of a large contiguous stack space as in C for continuations. Instead, we resort
to using small initial stacks and growing the stacks on demand. As a result,
OCaml functions, irrespective of whether they use effect handlers, need to
perform stack overflow checks and external C functions (which do not have stack
overflow checks) must be performed on a separate system stack. Additionally, we
must generate DWARF stack unwind tables for stacks that may be non-contiguous.
In this work, we develop the compiler and runtime support for implementing
efficient effect handlers for OCaml that satisfy these requirements.
